---
title: "Crowdedness at the Campus Gym"
author: "Justin Dong, David Pham"
date: "1/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(installr)
library(ggplot2)
library(knitr)
gym_data <- read.csv("../data/data.csv")
source("../source/table.R")
source("../source/chart_1.R")
source("../source/chart_3.R")
source("../source/summary.R")
```

## About Our Data
Our data set, "Crowdedness at the Campus Gym," contains `r get_observations()` observations total with `r get_metrics()` variables that were measured about different traffic levels at the Berkeley campus gym. The most amount of people inside the gym is `r get_max_crowdedness()` while the average amount of people present at the gym is `r get_average_crowdedness()`. The average temperature of the location of the gym is `r get_average_temperature()`, which is much higher than Seattles. 

## Table
```{r}
kable(sorted[1:50, ], caption = "Aggregate Information Table")
```

The table shows a summary of data 

```{r heatmap, echo = FALSE}
plot(average_people_chart)
```

This chart shows a heat mapping of every weekday and the average amount of people you can expect in the gym at any time. 

```{r scatterplot, echo = FALSE}
plot(scatterplot)
```

This scatterplot shows a plot of number of people at the gym compared to temperature
